Stack Safety is a Security Property

### 2021-04-13 tex/main.tex
remove foolish comment

\apt{How about an example incorporating temporal safety violations due to
   reading uninitialized values?}

@@

Our model provides only limited support for handling fully first-class pointers into
stack frames, e.g., pointers obtained by taking the address of a local variable.
Unlike the case for pass-by-reference, there is no easy way to model the intended sharing behavior
of such pointers in terms of stack frame activation patterns.  The best approximation we can make is to
treat a location whose address is taken as unsealed for the rest of its lifetime, i.e., until
its original owner deallocates it (typically by returning).  This prevents violations
of temporal safety (use after free), but still permits callees to access the location without having
been explicitly given a pointer to it.  Preventing the latter kind of abuse
is the provence of a fine-grained memory safety policy, e.g. based on capabilities
(implemented by tags or some other mechanism); we believe it is beyond the scope of stack safety
\emph{per se}.

>>>>

@@

Our model provides only limited support for handling fully first-class pointers into
stack frames, e.g., pointers obtained by taking the address of a local variable.
Unlike the case for pass-by-reference, there is no easy way to model the intended sharing behavior
of such pointers in terms of stack frame activation patterns.  The best approximation we can make is to
treat an address-taken variable in the same way as a passed argument, with the additional property
that it remains accessible at \emph{all} stack depths above the caller. 
This prevents most violations of temporal safety, although stale pointers can still be
used in certain corner cases. \apt{Trying not to spell out the details, which are complex.}
More seriously, callees are permitted to access the location without having
been explicitly given a pointer to it.  Preventing the latter kind of abuse
is the provence of a fine-grained memory safety policy, e.g. based on capabilities
(implemented by tags or otherwise); we argue it is beyond the scope of stack safety
\emph{per se}.
